### 2017-09-28 icde/sec-exp.tex

We constructed two sets of ground-truth importance orders of article pairs with \recom and \fcita.

\noindent
(1) \recom assumes that scholarly articles with more recommendations are of higher importance.
%
%evaluates the importance of scholarly articles by the numbers of recommendations (from textbooks and/or university course reading lists).
We used the numbers of recommendations of 93 articles on \aan~\cite{Liang16AAAI}, %which are recommended by 2 to 10 times,
and, by exact title matching, %then matched articles in \aminer and \magdata with titles.  Finally, we
generated (2133, 966, 1972) scholarly article pairs on (\aan, \aminer, \magdata), respectively.
%These articles were further matched into \aminer and \magdata through titles, which generated 966 and 1,972 article pairs for \aminer and \magdata, respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t!]
%\vspace{-2ex}
\label{tab-result}
\begin{center}
\caption{\small Accuracy tests with \recom}
%\begin{small}
%\vspace{-.5ex}
\begin{tabular}{|c|c|c|c|c|}
\hline
{\bf Datasets}   &  \hspace{1ex}\pagerank\hspace{1ex}     & \hspace{1ex}\futurerank\hspace{1ex}  &  \hspace{1ex}\hhgrank\hspace{1ex}  &   \hspace{1ex}\ensemblerank\hspace{1ex}    \\
\hline \hline
\aan  & $0.671$   & $0.738$   & $0.758$     & {\bf 0.805}      \\  %\hline
\aminer  & $0.651$   & $0.729$   & $0.730$     & {\bf 0.778}      \\ %\hline
\magdata  & $0.615$   & $0.655$   & $0.658$     & {\bf 0.680}      \\ \hline
\end{tabular}
%\vspace{-.5ex}
%\end{small}
\end{center}
\vspace{-4ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

@@

%varying difference of future citation count in benchmark
\etitle{Exp-2.3}.
%\stitle{Exp-2.3}.
To evaluate the effectiveness of ranking \wrt\ {\em the difference of past and future citations},
we varied the difference $dif$ of past and future citation counts from 1 to 7, while fixed $Y_s$ to default values of three datasets and $T_i=+\infty$. The results of \PairAcc are reported in Figs.~\ref{exp-aan-fcdiff}, \ref{exp-aminer-fcdiff} and \ref{exp-mag-fcdiff}.

@@

\stitle{Exp-4: Impacts of parameters}.
%\subsubsection{Exp-4: Impacts of parameters}.
In the last set of tests, we evaluated the impacts of time decaying factor $\sigma$, importance weighting factor $\lambda$, aggregating parameters $\alpha$ and $\beta$, and the TWPageRank. We fixed these parameters as well as $Y_s$ to their default values, used the TWPageRank proposed in this work by default, and tested the \PairAcc with the entire \recom and \fcita (\ie $T_i=+\infty$, $dif=1$).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Accuracy tests using different components with \recom (rows 2--4) and \fcita (rows 5--7).}
\label{tab-recom}
%\begin{small}
%\vspace{-.5ex}
\begin{tabular}{|c| c |c | c|}
\hline
{\bf Datasets} & {\bf C}\hspace{5ex}{\bf V}\hspace{5ex}{\bf A} & {\bf CV}\hspace{3ex}{\bf CA}\hspace{3ex}{\bf VA} & {\bf CVA} \\
\hline \hline
% \recom
\aan & 0.752 \ 0.616 \ 0.649 & 0.809 \ 0.764 \ 0.747 & {\bf 0.810} \\
\aminer & 0.735 \  0.581 \  0.640 & 0.784 \ 0.749 \ 0.729 & {\bf 0.785} \\
\magdata & 0.635 \ 0.534 \ 0.553 & 0.697 \ 0.673 \  0.648 & {\bf 0.698} \\ \hline
% \ficta
\aan & 0.785 \ 0.557 \ 0.761 & 0.849 \ 0.866 \ 0.771 & {\bf 0.870} \\
\aminer & 0.713 \  0.603 \  0.725 & 0.843 \ 0.847 \ 0.740 & {\bf 0.856} \\
\magdata & 0.736 \ 0.628 \ 0.718 & 0.848 \ 0.857 \ 0.751 & {\bf 0.874} \\
\hline
\end{tabular}
%\end{small}
\end{center}
\vspace{-4ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

>>>>

We constructed two sets of ground-truth importance orders of article pairs, referred to as  \recom and \fcita.

\noindent
(1) \recom assumes that scholarly articles with more recommendations are of higher importance.
%
%evaluates the importance of scholarly articles by the numbers of recommendations (from textbooks and/or university course reading lists).
We used the number of recommendations of 93 articles on \aan~\cite{Liang16AAAI}, %which are recommended by 2 to 10 times,
and, by exact title matching, %then matched articles in \aminer and \magdata with titles.  Finally, we
generated (2133, 966, 1972) scholarly article pairs on (\aan, \aminer, \magdata), respectively.
%These articles were further matched into \aminer and \magdata through titles, which generated 966 and 1,972 article pairs for \aminer and \magdata, respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t!]
%\vspace{-2ex}
\label{tab-result}
\begin{center}
\caption{\small Accuracy evaluation with \recom}
%\begin{small}
%\vspace{-.5ex}
\begin{tabular}{|c|c|c|c|c|}
\hline
{\bf Datasets}   &  \hspace{1ex}\pagerank\hspace{1ex}     & \hspace{1ex}\futurerank\hspace{1ex}  &  \hspace{1ex}\hhgrank\hspace{1ex}  &   \hspace{1ex}\ensemblerank\hspace{1ex}    \\
\hline \hline
\aan  & $0.671$   & $0.738$   & $0.758$     & {\bf 0.805}      \\  %\hline
\aminer  & $0.651$   & $0.729$   & $0.730$     & {\bf 0.778}      \\ %\hline
\magdata  & $0.615$   & $0.655$   & $0.658$     & {\bf 0.680}      \\ \hline
\end{tabular}
%\vspace{-.5ex}
%\end{small}
\end{center}
\vspace{-4ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

@@

%varying difference of future citation count in benchmark
\etitle{Exp-2.3}.
%\stitle{Exp-2.3}.
To evaluate the effectiveness of ranking \wrt\ {\em the difference of past and future citations},
we varied the difference $dif$ of past and future citation counts from 1 to 7, while fixed $Y_s$ to default values of three datasets and $T_p=+\infty$. The results of \PairAcc are reported in Figs.~\ref{exp-aan-fcdiff}, \ref{exp-aminer-fcdiff} and \ref{exp-mag-fcdiff}.

@@

\stitle{Exp-4: Impacts of parameters}.
%\subsubsection{Exp-4: Impacts of parameters}.
In the last set of tests, we evaluated the impacts of time decaying factor $\sigma$, importance weighting factor $\lambda$, aggregating parameters $\alpha$ and $\beta$, and the TWPageRank. We fixed these parameters as well as $Y_s$ to their default values, used the TWPageRank proposed in this work by default, and tested the \PairAcc with the entire \recom and \fcita (\ie $T_p=+\infty$, $dif=1$).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Accuracy evaluation using different components with \recom (rows 2--4) and \fcita (rows 5--7).}
\label{tab-recom}
%\begin{small}
%\vspace{-.5ex}
\begin{tabular}{|c| c |c | c|}
\hline
{\bf Datasets} & {\bf C}\hspace{5ex}{\bf V}\hspace{5ex}{\bf A} & {\bf CV}\hspace{3ex}{\bf CA}\hspace{3ex}{\bf VA} & {\bf CVA} \\
\hline \hline
% \recom
\aan & 0.752 \ 0.616 \ 0.649 & 0.809 \ 0.764 \ 0.747 & {\bf 0.810} \\
\aminer & 0.735 \  0.581 \  0.640 & 0.784 \ 0.749 \ 0.729 & {\bf 0.785} \\
\magdata & 0.635 \ 0.534 \ 0.553 & 0.697 \ 0.673 \  0.648 & {\bf 0.698} \\ \hline
% \ficta
\aan & 0.785 \ 0.557 \ 0.761 & 0.849 \ 0.866 \ 0.771 & {\bf 0.870} \\
\aminer & 0.713 \  0.603 \  0.725 & 0.843 \ 0.847 \ 0.740 & {\bf 0.856} \\
\magdata & 0.736 \ 0.628 \ 0.718 & 0.848 \ 0.857 \ 0.751 & {\bf 0.874} \\
\hline
\end{tabular}
%\end{small}
\end{center}
\vspace{-4ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

### 2017-09-28 icde/sec-model.tex

\stitle{Time-Weighted PageRank (TWPageRank)}. Most previous work simply exploits temporal information in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}. We rethink the usage of time information in terms of the impacts of scholarly articles.
Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with the citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1. Though the number of citations is an indicator of the impact of articles~\cite{WangSB13,Garfield471}, its impact is time-dependent and is not simply in the form of exponential decay.
In general, {\em the impact of an article tends to decay with time after the peak time only}. That is, the impacts of articles directly decay with time only for those in {\em MonDec}, and decay with time after the peak time for those in {\em PeakInit}, {\em PeakLate} and {\em PeakMul}, and do not decay for ones in {\em MonIncr} (which is rare).
%Otherwise, its impact is fixed as a constant number. %, since we argue that the increment of its citations during this period is mainly due to the increase of its popularity.
Also observe that {\em each individual article has its own peak time} as articles may reach their citation peaks in different patterns and time.
%using the peak year in Fig.~\ref{fig-citation} is not appropriate for all articles. On the contrary, we compute a peak year for each article.

@@

\begin{figure}
\centering
\includegraphics[scale=0.48]{fig/yearly-references.eps}
\vspace{-1ex}
\caption{\small Citation statistics of scholarly articles that reports the (logscale) percentage of the number of citations of each year \wrt\ the total number of citations  in  \aan, \aminer and \magdata, respectively.}
\label{fig-reference}
\vspace{-3ex}
\end{figure}

@@

For scholarly article ranking, $T_u$ is the publication time of article $u$ and $Peak_v$ should be ideally set to the time when article $v$ has the highest impacts. Basically, it could simply be the year when article $v$ obtains the largest number of citations. However, recent work reveals that the volume of scientific publications as well as the number of citations grow exponentially with time~\cite{Dong2017KDD,BornmannM15}. We also collect and report the citations statistics on three scholarly datasets in Fig.~\ref{fig-reference}, which verifies the exponential distribution. Hence, we adopt the {\em scaled} number of citations $\Psi_v^{(t)}=\Phi_v^{(t)} / \log Z^{(t)}$ such that $\Phi_v^{(t)}$ and $Z^{(t)}$ are the number of citations of article $v$ at year $t$ and the total number of citations at year $t$, respectively. The peak time $Peak_v$ is the time that maximizes $\Psi_v^{(t)}$.
%(\aan, \aminer and \magdata)
% since scholarly data is dynamic and continuously growing
%, and the increased number of references of each article over time
%Recent work observes that the volume of scientific publications doubled every 12 years between 1900 and 2015~\cite{Dong2017KDD}. It is not surprising that the number of references also grows exponentially~\cite{BornmannM15}.

@@

\vspace{-1ex}
\begin{small}
\begin{equation}
\label{eq-twpr-update}
PR^{(t)}=d M^T  PR^{(t-1)} + (1-d) e/n.
\end{equation}
\end{small}
%
\noindent
Here $PR^{(k)}$ is the TWPageRank vectors after $k$ iterations,  $M$ is the transition matrix such that $M_{u,v}=w(u,v)/W(u)$ and  $e$ is an $n$-dimensional all-one vector $[1]_{n\times1}$.

@@

\sstab(2)  The popularity of an article is the sum of all its citations' freshness, \ie the closeness to the current year:

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-pop}
Pop_c(v) = \sum_{{(u,v)\in E^c}} {e^{\sigma (T_0-T_u)}}.
\end{equation}
\end{small}
\noindent
Here $T_0$ is the current year, \ie the latest $T_u$ among all articles in $V^c$, $\sigma$ is the negative decaying factor used in Eq.~(\ref{eq-infl-weights}), and $e^{\sigma (T_0-T_u)}$ represents the freshness of citation $(u,v)$.

@@

\stitle{Remark}. This work follows the graph-based formalization, and further develops efficient batch and incremental algorithms based on graphs for scholarly article ranking (Sections~\ref{sec-alg} \& \ref{sec-incAlg}). However, it is also possible to learn a discriminative model that directly optimizes certain loss functions for ranking, similar to \cite{Richardson06:BPR} for ranking Web pages.

>>>>

\stitle{Time-Weighted PageRank (TWPageRank)}. Most previous work simply exploits temporal information in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}. We rethink the usage of time information in terms of the impacts of scholarly articles.
Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with a single citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1. Though the number of citations is an indicator of the impact of an article~\cite{WangSB13,Garfield471}, its impact is time-dependent and is not simply in the form of exponential decay.
In general, {\em the impact of an article tends to decay with time after the peak time only}. That is, the impacts of articles directly decay with time only for those in {\em MonDec}, and decay with time after the peak time for those in {\em PeakInit}, {\em PeakLate} and {\em PeakMul}, and do not decay for ones in {\em MonIncr} (which is rare).
%Otherwise, its impact is fixed as a constant number. %, since we argue that the increment of its citations during this period is mainly due to the increase of its popularity.
Also observe that {\em each individual article has its own peak time} as articles may reach their citation peaks in different patterns and time.
%using the peak year in Fig.~\ref{fig-citation} is not appropriate for all articles. On the contrary, we compute a peak year for each article.

@@

\begin{figure}
\centering
\includegraphics[scale=0.48]{fig/yearly-references.eps}
\vspace{-1ex}
\caption{\small Citation statistics of scholarly articles that reports the (logscale) percentage of the number of citations of each year \wrt\ the total number of citations on \aan, \aminer and \magdata, respectively.}
\label{fig-reference}
\vspace{-3ex}
\end{figure}

@@

For scholarly article ranking, $T_u$ is the publication time of article $u$ and $Peak_v$ should be ideally set to the time when article $v$ has the highest impacts. Basically, it could simply be the year when article $v$ obtains the largest number of citations. However, recent work reveals that the volume of scientific publications as well as the number of citations grow exponentially with time~\cite{Dong2017KDD,BornmannM15}. We also collect and report the citation statistics on three scholarly datasets in Fig.~\ref{fig-reference}, which verifies the exponential distribution. Hence, we adopt the {\em scaled} number of citations $\Psi_v^{(t)}=\Phi_v^{(t)} / \log Z^{(t)}$ such that $\Phi_v^{(t)}$ and $Z^{(t)}$ are the number of citations of article $v$ at year $t$ and the total number of citations at year $t$, respectively. The peak time $Peak_v$ is the time that maximizes $\Psi_v^{(t)}$.
%(\aan, \aminer and \magdata)
% since scholarly data is dynamic and continuously growing
%, and the increased number of references of each article over time
%Recent work observes that the volume of scientific publications doubled every 12 years between 1900 and 2015~\cite{Dong2017KDD}. It is not surprising that the number of references also grows exponentially~\cite{BornmannM15}.

@@

\vspace{-1ex}
\begin{small}
\begin{equation}
\label{eq-twpr-update}
PR^{(t)}=d M^T  PR^{(t-1)} + (1-d) e/n.
\end{equation}
\end{small}
%
\noindent
Here $PR^{(k)}$ is the TWPageRank vector after $k$ iterations,  $M$ is the transition matrix such that $M_{u,v}=w(u,v)/W(u)$ and  $e$ is an $n$-dimensional all-one vector $[1]_{n\times1}$.

@@

\sstab(2)  The popularity of an article is the sum of all its citation freshness, \ie the closeness to the current year:

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-pop}
Pop_c(v) = \sum_{{(u,v)\in E^c}} {e^{\sigma (T_0-T_u)}}.
\end{equation}
\end{small}
\noindent
Here $T_0$ is the current year, \ie the largest $T_u$ among all articles in $V^c$, $\sigma$ is the negative decaying factor used in Eq.~(\ref{eq-infl-weights}), and $e^{\sigma (T_0-T_u)}$ represents the freshness of citation $(u,v)$.

@@

\stitle{Remarks}. This work follows the graph-based formalization, and further develops efficient batch and incremental algorithms based on graphs for scholarly article ranking (Sections~\ref{sec-alg} \& \ref{sec-incAlg}). However, it is also possible to learn a discriminative model that directly optimizes certain loss functions for ranking, similar to \cite{Richardson06:BPR} for ranking Web pages.

### 2017-09-28 icde/sec-related.tex

PageRank \cite{Brin98:PageRank} and its extensions have been extensively used for citation analyses \cite{Waltman2014}. While PageRank equally propagates scores along outlinks, Weighted PageRank extends PageRank by distributing scores based on certain criteria such as popularity of pages~\cite{Xing04:WPR} or authority of authors~\cite{Ding11}. Both these approaches fail to capture the time-dependent characteristics, a key factor for scholarly article ranking. There has been work extending temporal information into PageRank, \eg exponential decayed weights~\cite{Li08TSRanking}, exponential decayed initial vector~\cite{WalkerXKM07} and time-dependent weights based on co-authorship~\cite{FIALA2012370}. Different from previous work, the Time-Weighted PageRank of this work discriminately propagates scores in terms of citation statistics.

>>>>

PageRank \cite{Brin98:PageRank} and its extensions have been extensively used for citation analyses \cite{Waltman2014}. While PageRank equally propagates scores along outlinks, Weighted PageRank extends PageRank by distributing scores based on certain criteria such as popularity of pages~\cite{Xing04:WPR} or authority of authors~\cite{Ding11}. Both these approaches fail to capture the time-dependent characteristics, a key factor for scholarly article ranking. There has been work extending temporal information into PageRank, \eg exponentially decayed weights~\cite{Li08TSRanking}, exponentially decayed initial vectors~\cite{WalkerXKM07} and time-dependent weights based on co-authorship~\cite{FIALA2012370}. Different from previous work, the Time-Weighted PageRank of this work discriminately propagates scores in terms of citation statistics.
